---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flexl

<!-- badges: start -->
<!-- badges: end -->

The goal of flexl is to ...

## Installation

To improve speed of C++ code, we need to switch off debugging.
In development, can do this by running

```{r, eval = FALSE}
pkgbuild::compile_dll(debug = FALSE)
devtools::load_all()
```

(installing the package with `install.packages` switches off debugging
automatically).

When compiling, I set the Makevars (`~/.R/Makevars`)
to 
```
CPPFLAGS = -w
```
to switch off the warnings. This was necessary because the code 
was very slow to compile if all warnings were printed (because of things included
from Boost and Eigen).

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(flexl)
## basic example code
```
