---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flexl


The goal of flexl is to implement flexible models
for simple longitudinal data. 
Given repeated observations on different subjects, we
model how the mean response for each subject varies over time. 

Writing $Y_{ij}$ for the observation on subject $i$ at time point $t_{ij}$, we model
$Y_{ij} = \mu_i(t_{ij}) + \epsilon_{ij},$
where $\mu_i(.)$ is a function describing how the mean response
for subject $i$ varies over time, and
$\epsilon_{ij} \sim N(0, \sigma^2)$ are independent error terms.
Our interest is in estimating the subject-specific
mean functions $\mu_i(.)$. 
In doing this, we allow flexible dependence on time, and make
 similarities between these curves to improve estimation.
 
Details of the methods used by flexl
are given in [this preprint](https://arxiv.org/abs/2401.11827).

## Installation

flexl can be installed by using

```{r, eval = FALSE}
devtools::install_github("heogden/flexl")
```

On Windows, this does not currently work, so please follow [these
instructions](https://github.com/heogden/flexl/issues/1#issue-2542522879)
as a temporary workaround.

## Example

For demonstration purposes, we use some
simulated longitudinal data, with 20 subjects
and 10 observations per subject

```{r, message = FALSE}
library(flexl)

data_full <- simulate_1dv(1, -0.5, 0.1, 0.5, 0.1, 20, 10)
data <- data_full$data
```

The data is in the format needed by flexl: it contains
columns `c` (an identifier for the subject),
`x` (the time the observation was made)
and `y` (the response).

We can plot the data:

```{r, message = FALSE}
library(tidyverse)

ggplot(data, aes(x = x, y = y)) +
    geom_point() +
    facet_wrap(vars(c), ncol = 5) +
    xlab("Time") +
    ylab("Response")

```
We can then fit the model using flexl:

```{r}
mod <- fit_flexl(data)
```

We can then plot out our estimated
subject-specific mean curves, with 
pointwise 95% confidence intervals.
Since this is simulated data, we can compare the
fitted mean curves against the true mean curves.

```{r}
pred_data <- data_full$pred_data %>%
    mutate(mu_c_hat = predict_flexl(mod,
                                    newdata = list(x = x, c = c),
                                    interval = TRUE))

ggplot(pred_data, aes(x = x)) +
    geom_line(aes(y = mu_c_hat$estimate)) +
    geom_ribbon(aes(ymin = mu_c_hat$lower, ymax = mu_c_hat$upper),
                alpha = 0.3) + 
    geom_line(aes(y = mu_c), linetype = "dashed") +
    facet_wrap(vars(c), ncol = 5) +
    xlab("Time") +
    ylab("Subject-specific mean")
```

In this simulated example, the fitted mean curves (solid lines)
and the true mean curves (dashed lines) match closely.
The confidence intervals are narrow in this case, 
but contain the true mean most of the time.
